Motor Learning Without Moving

### 2018-07-30 ManuscriptMaterials.Rmd
clean up code for loading packages, labeled some chunks

@@

```{r}
LMEmethod <- 'Satterthwaite'
# options: 'Satterthwaite', 'chi-squared'
```

@@

```{r}
plotBlinkDetection()
```

@@

```{r}
blinks <- load.DownloadDataframe(informationURLs['blinkdetect'],'blinkdetect_exposure.csv')
OKparticipants <- blinks$participant[which(blinks$rotated_b == 1 & blinks$performance > 0.65)]
```

@@

```{r}
selectPerformance <- TRUE
```

@@

```{r}
participants <- load.DownloadDataframe(informationURLs['demographics'],'participants_exposure.csv')
if (selectPerformance) {
  participants <- participants[which(participants$participant %in% OKparticipants),]
}
```

@@

```{r}
print(c('mean'=mean(participants$age), 'sd'=sd(participants$age)))
```

@@

```{r}
print(table(participants$sex))
```

@@

## Pearons Correlations

@@

```{r create_svgs, cache=FALSE, include=FALSE}
# This chunk creates SVG files but shouldn't show up in the PDF / HTML 
plotReachAftereffects(generateSVG=TRUE,
                      selectPerformance=selectPerformance)
plotLocalization(classicOnline=TRUE,
                 generateSVG=TRUE, 
                 selectPerformance=selectPerformance)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE, 
                                               selectPerformance=selectPerformance)
#plotBlinkDetection(generateSVG=TRUE)
```

>>>>

And we try to import some packages we use here:

```{r require_lme_packages}
required.packages = c('lme4', 'lmerTest', installmissing=FALSE)
installRequire.Packages(required.packages)
```

Note: the packages `foreach` and `doParallel` will speed up the bootstrapping of peak fits, but the scripts will also run without.

Note: the package `svglite` is used to generate SVG files with figures, but the scripts will simply skip this if the package is not available.

@@

```{r set_LMEmethod}
LMEmethod <- 'Satterthwaite'
# options: 'Satterthwaite', 'chi-squared'
```

If `LMEmethod` is set as 'chi-squared', we need some other packages to be able to run this:

```{r requireChiSquared_packages}
required.packages = c('nlme', 'car')
installRequire.Packages(required.packages, installmissing=FALSE)
```

@@

```{r plotBlinkDetectionPerformance}
plotBlinkDetection()
```

@@

```{r selectHighPerformingParticipants}
blinks <- load.DownloadDataframe(informationURLs['blinkdetect'],'blinkdetect_exposure.csv')
OKparticipants <- blinks$participant[which(blinks$rotated_b == 1 & blinks$performance > 0.65)]
```

@@

```{r set_selectPerformance_variable}
selectPerformance <- TRUE
```

@@

```{r load_select_participantInfo}
participants <- load.DownloadDataframe(informationURLs['demographics'],'participants_exposure.csv')
if (selectPerformance) {
  participants <- participants[which(participants$participant %in% OKparticipants),]
}
```

@@

```{r age_stats}
print(c('mean'=mean(participants$age), 'sd'=sd(participants$age)))
```

@@

```{r sex_distribution}
print(table(participants$sex))
```

@@

## Pearson Correlations

@@

```{r create_svgs, cache=FALSE, include=FALSE}
# This chunk creates SVG files but shouldn't show up in the PDF / HTML 
plotReachAftereffects(generateSVG=TRUE,
                      selectPerformance=selectPerformance)
plotLocalization(classicOnline=TRUE,
                 generateSVG=TRUE, 
                 selectPerformance=selectPerformance)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE, 
                                               selectPerformance=selectPerformance)
```
